---
title: "Text: Words 2"
author: "Donovan Dean"
date: "`r Sys.Date()`"
editor: visual
format:
  html:
    embed-resources: true
    code-fold: true  # new
execute:
  echo: true
  message: false
  warning: false
---

```{r setup}
library(tidyverse)
library(rvest)
library(wordcloud)
library(tm)
library(tidytext)
library(SnowballC)
library(ggplot2)
```

# Romeo and Juliet

"Oh Romeo, Romeo, wherefore art thou Romeo?"

Full script - <http://shakespeare.mit.edu/romeo_juliet/full.html>

Let's explore...

1.  Whose name appears more often, Romeo or Juliet?
2.  Perform "pre-cleaning" on the file to remove extraneous characters.
3.  Identify which word appears most often in the text

# Read in Romeo and Juliet

```{r}
RandJ0 <- read_file("/Users/donovandean/Documents/Academics/Villanova University/Spring 2026/Data Science Tools (STAT8796)/Assignments/Homework/HW4/HW4 Instructions_files/RandJ.txt")
```

```{r}
#Referencing my own local path to see your results
RandJ0 <- read_file("Romeo and Juliet Entire Play.txt")
```

# Term Frequency

Whose name appears more often, Romeo or Juliet?{r}

```{r}
RandJ_format <- str_to_lower(RandJ0)
RandJ_remove_speaking <- RandJ_format |> 
  str_remove_all("\\*romeo\\*|\\*juliet\\*")

romeo_count <- str_count(RandJ_remove_speaking, "\\bromeo\\b") |> 
  sum()
juliet_count <- str_count(RandJ_remove_speaking, "\\bjuliet\\b") |> 
  sum()

tibble(name = c("Romeo", "Juliet"),
       frequency = c(romeo_count, juliet_count))
```

After removing the speaker labels so that only textual mentions were counted, Romeo (146) appears more frequently than Juliet (63) in the play.

# Pre-cleaning / Tokenize

Perform "pre-cleaning" on the file to remove extraneous characters.

**\[Code Comment\]** In this section you could reduce the length of code by combining your different steps into a single pipe. You can unnest, filter, join, and count in a single step. However, I imagine this made it easier to double check each step was working as intended.

Thanks for the feedback! And you are correct, I separated the cleaning steps so I could check that each parts were working correctly.

**\[Comment 1\]** Top 10 responses here will still help you validate but not take up too much space on your final PDF. This won't matter as much if you combine all steps into one pipe, as mentioned above.

```{r}
RandJ_tbl <- tibble(text = RandJ_remove_speaking)
RandJ_words <- RandJ_tbl |> 
  unnest_tokens(word, text)

RandJ_words_clean <- RandJ_words |> 
  filter(str_detect(word, "^[a-z]+$"))
head(RandJ_words_clean, 10)

data(stop_words)
RandJ_words_nostop <- RandJ_words_clean |> 
  anti_join(stop_words, by = "word")
head(RandJ_words_nostop, 10)

word_count <- RandJ_words_nostop |> 
  count(word, sort = TRUE)
head(word_count, 10)
```

# Wordcloud

In case we get here during in-class coding and you want to access what I have, here are two rds files...that I'll talk about when we get here.

```{r}
set.seed(123)

wordcloud(words = word_count$word,
          freq = word_count$n,
          max.words = 50,
          colors = brewer.pal(8, "Dark2"))
```

# n-grams

```{r}
RandJ_bigrams <- RandJ_tbl |> 
  unnest_tokens(bigrams, text, token = "ngrams", n = 2)

RandJ_bigrams_sep <- RandJ_bigrams |> 
  separate(bigrams, into = c("word1", "word2", sep = " "))

RandJ_bigrams_clean <- RandJ_bigrams_sep |> 
  filter(!word1 %in% stop_words$word,
         !word2 %in% stop_words$word)

RandJ_bigrams_final <- RandJ_bigrams_clean |> 
  unite(bigrams, word1, word2, sep = " ")
bigram_count <- RandJ_bigrams_final |> 
  count(bigrams, sort = TRUE)
head(bigram_count, 10)
```

# Visualization of n-grams

**\[Comment 2\]** You could potentially limit the results given so many words in the worldcloud, and try to introduce color. I see you're using slice_max, but it is not limiting to top 10 results. I also had my own challenges trying to group by different colors for different themes, like we did in class.

```{r}
bigram_count |> 
  slice_max(n, n = 10) |> 
  ggplot(aes(x = reorder(bigrams, n), y = n)) + 
  geom_col() + 
  coord_flip() + 
  labs(title = "Top 10 Bigrams in Romeo and Juliet",
       x = NULL,
       y = "Count")
```

The most frequent bigram is "friar laurence", reflecting the central role of Friar Laurence in the plot.

**\[Comment 3\]** Any other interesting bigrams? I also saw primarily proper nouns, but any non-stopwards that illustrate central themes of the text?

The most frequent bigram is "friar laurence," which makes sense given his importance in the play. Other common bigrams like "lady capulet" also point to major characters, so a lot of the results are driven by names. There are also phrases like "thou art," "thou hast," and "thou wilt," which reflect the older Shakespearean language rather than specific themes. Additionally, some bigrams such as "enter romeo" and "exeunt scene" come from stage directions, so overall the bigrams capture characters and structure more than broader thematic ideas.
