---
title: "Text: Words 2"
author: "Donovan Dean"
date: "`r Sys.Date()`"
editor: visual
format:
  html:
    embed-resources: true
    code-fold: true  # new
execute:
  echo: true
  message: false
  warning: false
---

```{r setup}
library(tidyverse)
library(rvest)
library(wordcloud)
library(tm)
library(tidytext)
library(SnowballC)
library(ggplot2)
```

# Romeo and Juliet

"Oh Romeo, Romeo, wherefore art thou Romeo?"

Full script - <http://shakespeare.mit.edu/romeo_juliet/full.html>

Let's explore...

1.  Whose name appears more often, Romeo or Juliet?
2.  Perform "pre-cleaning" on the file to remove extraneous characters.
3.  Identify which word appears most often in the text

# Read in Romeo and Juliet

```{r}
RandJ0 <- read_file("/Users/donovandean/Documents/Academics/Villanova University/Spring 2026/Data Science Tools (STAT8796)/Assignments/Homework/HW4/HW4 Instructions_files/RandJ.txt")
```

# Term Frequency

Whose name appears more often, Romeo or Juliet?{r}

```{r}
RandJ_format <- str_to_lower(RandJ0)
RandJ_remove_speaking <- RandJ_format |> 
  str_remove_all("\\*romeo\\*|\\*juliet\\*")

romeo_count <- str_count(RandJ_remove_speaking, "\\bromeo\\b") |> 
  sum()
juliet_count <- str_count(RandJ_remove_speaking, "\\bjuliet\\b") |> 
  sum()

tibble(name = c("Romeo", "Juliet"),
       frequency = c(romeo_count, juliet_count))
```

After removing the speaker labels so that only textual mentions were counted, Romeo (146) appears more frequently than Juliet (63) in the play.

# Pre-cleaning / Tokenize

Perform "pre-cleaning" on the file to remove extraneous characters.

```{r}
RandJ_tbl <- tibble(text = RandJ_remove_speaking)
RandJ_words <- RandJ_tbl |> 
  unnest_tokens(word, text)

RandJ_words_clean <- RandJ_words |> 
  filter(str_detect(word, "^[a-z]+$"))
head(RandJ_words_clean, 20)

data(stop_words)
RandJ_words_nostop <- RandJ_words_clean |> 
  anti_join(stop_words, by = "word")
head(RandJ_words_nostop, 20)

word_count <- RandJ_words_nostop |> 
  count(word, sort = TRUE)
head(word_count, 10)
```

# Wordcloud

In case we get here during in-class coding and you want to access what I have, here are two rds files...that I'll talk about when we get here.

```{r}
set.seed(123)

wordcloud(words = word_count$word,
          freq = word_count$n,
          max.words = 100)
```

# n-grams

```{r}
RandJ_bigrams <- RandJ_tbl |> 
  unnest_tokens(bigrams, text, token = "ngrams", n = 2)

RandJ_bigrams_sep <- RandJ_bigrams |> 
  separate(bigrams, into = c("word1", "word2", sep = " "))

RandJ_bigrams_clean <- RandJ_bigrams_sep |> 
  filter(!word1 %in% stop_words$word,
         !word2 %in% stop_words$word)

RandJ_bigrams_final <- RandJ_bigrams_clean |> 
  unite(bigrams, word1, word2, sep = " ")
bigram_count <- RandJ_bigrams_final |> 
  count(bigrams, sort = TRUE)
head(bigram_count, 10)
```

# Visualization of n-grams

```{r}
bigram_count |> 
  slice_max(n, n = 10) |> 
  ggplot(aes(x = reorder(bigrams, n), y = n)) + 
  geom_col() + 
  coord_flip() + 
  labs(title = "Top 10 Bigrams in Romeo and Juliet",
       x = NULL,
       y = "Count")
```

The most frequent bigram is "friar laurence", reflecting the central role of Friar Laurence in the plot.
